---
title: "French Government Scholarships to Foreign Students"
author: "Karine G"
date: "28 septembre 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Introduction

French government scholarships are allocated by the Ministry for Europe and Foreign Affairs for studies, training courses and language courses in France. 

https://www.diplomatie.gouv.fr/en/coming-to-france/studying-in-france/finance-your-studies-scholarships/

We have here a look at their geographical repartition by world region 2006-2011 thanks to open data published by the French authorities.

## French government scholarships to foreign students


The dataset is a csv file provided by the official French governmental platform for open data and features the number of scholarships to foreign students provided by the French government from 2006 through 2011. 

https://www.data.gouv.fr/fr/datasets/boursiers-du-gouvernement-francais/#_

### Importing the data 

With a glimpse into a subset of the original dataset.

```{r dataset}
### Source: https://www.data.gouv.fr/fr/datasets/boursiers-du-gouvernement-francais/#_ 
dataUrl <- 'http://www.data.gouv.fr/fr/datasets/r/dd3b4807-d90c-46fe-b03a-2ad250db979f'
download.file(dataUrl, "myData.csv")
globalData <- read.table("myData.csv", sep=";")
print(globalData[1:11,1:4])
```

Opening libraries: R.utils, data.table, tidyr, dplyr, readr, ggplot2, sf, RColorBrewer. 

```{r libraries, echo= TRUE, include = FALSE}
library(R.utils)
library(data.table)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(sf)
library(RColorBrewer)
```

## Tidying the data
We subselect the rows and columns in order to have a dataset we can work on. To get useful numbers to do computations with, we must convert those in the dataset to numeric (and transit through the character format for that purpose, - while applying some regex through the "sub" function in order to remove blanks within large numbers).

```{r tidying_dataframe, echo=TRUE}
tidyData <- globalData[4:15,2:7] %>% 
        apply(2, as.character) %>% 
        sub(" ", "", .) %>% 
        apply(2, as.numeric) %>%
        as.data.frame(.)
```

Then, let's get a more conventional presentation with rows, not columns, indicating years. Hence, a transposing of the matrix through the 't' function is effected. In order to use ggplot2 conveniently, years are added as a column in itself. Normalized labels are used for the regions instead of the full names.

```{r final_tidying, echo=TRUE}

Years <- as.factor(as.character(c(2006:2011)))
finalTidy <- as.data.frame(t(tidyData)) %>% 
        cbind(Years, .)
Regions <- c("Years", "EU", "EurNotEU", "Total_Eur", "Am_N", "Total_Am", "Total_Asia_O", "Middle_E", "AfSubS_F", "AfSubS_nF","Total_AfSubS", "Maghreb", "Total_Ge")
colnames(finalTidy) <- Regions
rownames(finalTidy) <- Years
print(finalTidy)
```

### Data vizualization

```{r vizualization, echo= TRUE}

data_Eur <- cbind(finalTidy[,c(1,4)], Region=rep("Europe", 6))
data_Am <- cbind(finalTidy[,c(1,6)], Region=rep("America", 6))
data_Asia <- cbind(finalTidy[,c(1,7)], Region=rep("Asia/OCeania", 6))
data_ME <- cbind(finalTidy[,c(1,8)], Region=rep("Middle East", 6))
data_Afr <- cbind(finalTidy[,c(1,11)], Region=rep("Sub-Saharan Africa", 6))
data_Magh <- cbind(finalTidy[,c(1,12)], Region=rep("Maghreb", 6))


names(data_Eur)<- c("Years", "Total", "Region")
names(data_Am)<- c("Years", "Total", "Region")
names(data_Asia)<- c("Years", "Total", "Region")
names(data_ME)<- c("Years", "Total", "Region")
names(data_Afr)<- c("Years", "Total", "Region")
names(data_Magh)<- c("Years", "Total", "Region")

long_Data <- rbind(data_Afr, data_Am, data_Asia, data_Eur, data_Magh, data_ME)

#### DATA VIZ ####

ScholPlot <- ggplot(data=long_Data) + geom_point(aes(x=Years, y=Total, color = Region, size= 10)) +
        geom_line(aes(x=Years, y=Total, group = Region)) + guides(size=FALSE)
print(ScholPlot)

ggsave('ScholPlot.png', width = 16, height = 9, dpi = 100)
```


## Creating a map

Preparing the shapefile.  
MapSource http://thematicmapping.org/downloads/TM_WORLD_BORDERS_SIMPL-0.3.zip 
Shapefile is extracted from zip and used for the next steps.


``` {r map and regions, echo = TRUE }


region_location <- "C:/Users/Kroutz-/Dropbox/MOOCS/DATA/DATA_Knight/WORLD_SIMPL/TM_WORLD_BORDERS_SIMPL-0.3.shp"


theRegions <- st_read(region_location)

myRegions <- tbl_df(theRegions) %>%
        select(NAME, SUBREGION, LON, LAT, geometry) %>%
        mutate(SUBREGION=as.factor(SUBREGION), NAME=as.character(NAME))




```` 

We must merge our own geographic repartition with the one from the shapefile. The shapefile indeed lists the world countries and groups them by regions and subregions (additional columns), but those don't match the world regions from our initial dataset. Some investigation into the data is here necessary.

So we create here a ne data frame "OrderedList" to order subregions by number and thus check the list (not published here, see the created data frame "OrderedList" if you want to reproduce step by step). This makes it easily then to peruse the document and find the logic behind the numbers, - and thus reassign countries by subregion number to "our" subregions from the original list we have for scholarships as a next step.


```{r adapting shapefile to original dataset, echo = TRUE}


OrderedList <- myRegions[order(myRegions$SUBREGION),]


```

The shapefile's subregions (represented by specific numbers) are browsed through in this OrderedList data frame, - and reassigned to our #own categories (some countries have to be extracted from their "subregion" and individually reassigned). Here what we found:

Middle East: 145 (+ Iran)
EUR:  39,151,154,155
Maghreb:   15+Egypt+Sudan
AfSubS:   11, 14, 17, 18
Asia_0:   30,34, 35, 53, 54, 57, 61, 143


```{r shapefile to original dataset, echo = TRUE}

myRegions <- mutate(myRegions, Regions=" ")
myRegions$Regions[myRegions$SUBREGION =="0"] <- "Antarctica"
myRegions$Regions[myRegions$SUBREGION %in% c(39, 151, 154, 155)] <- "Europe"
myRegions$Regions[myRegions$SUBREGION %in% c(11, 14, 17, 18)] <- "Sub-Saharan Africa"
myRegions$Regions[myRegions$SUBREGION %in% c(30, 34, 35, 53, 54, 57, 61, 143)] <- "Asia & Oceania"
myRegions$Regions[myRegions$SUBREGION %in% c(5, 13, 21, 29)] <- "America"
myRegions$Regions[myRegions$SUBREGION == 145] <- "Middle East"
myRegions$Regions[myRegions$SUBREGION == 15] <- "Maghreb"

myRegions$Regions[myRegions$NAME=="Iran (Islamic Republic of)"]<- "Middle East"
myRegions$Regions[myRegions$NAME=="Sudan"]<- "Sub-Saharan Africa"
myRegions$Regions[myRegions$NAME=="Egypt"]<- "Middle East"

#Now we add the 2011 figures for those regions as those are the ones we want to map.
myRegions$schol <- myRegions$Regions
myRegions$schol[myRegions$schol == "Europe"]<- 2755
myRegions$schol[myRegions$schol == "Middle East"]<- 1697
myRegions$schol[myRegions$schol == "Maghreb"]<- 2897
myRegions$schol[myRegions$schol == "Sub-Saharan Africa"]<- 2906
myRegions$schol[myRegions$schol == "Asia & Oceania"]<- 2662
myRegions$schol[myRegions$schol == "America"]<- 1770
myRegions$schol[myRegions$schol == "Antarctica"]<- NA

```

Now, let's do a map.

```{r LON and LAT for map, out.width="120%", echo = TRUE}


# Substituting the regional mean for LON and LAT,
# & Correcting LON/LAT for Asia & Oceania and Antartica Regions 
# to have them more conveniently placed on the map.

myRegions_notRegrouped <- myRegions
myRegions <- myRegions %>%
        group_by(Regions) %>%
        mutate(LON = mean(LON), LAT = mean(LAT),
               LON = case_when(Regions == "Asia & Oceania" ~ LON+50, TRUE  ~ LON),
               LAT = case_when(Regions == "Antarctica" ~ LAT-50, TRUE ~ LAT))

```

Let's make a choropleth map with this.

```{r drawing a map, out.width="120%", echo = TRUE}

myRegions$schol <- as.numeric(myRegions$schol)

myColors <- brewer.pal(12,"Set3") 
names(myColors) <- levels(as.factor(myRegions$Regions))

myMap <- ggplot(myRegions) + geom_sf(aes(fill=schol,color = Regions))+
        scale_fill_distiller(direction = 1, 
                             name =" Number of Scholarships", palette="Oranges")+
        labs(caption="Number of Scholarships Given by World Region in 2016", 
             subtitle="Scholarships to Foreign Students by the French Government")+
        geom_label(aes(x=LON, y=LAT), 
                   color="black", 
                   label=toupper(myRegions$Regions), size=1.7)+
        xlab("") + ylab("") +
        guides(color = FALSE)

print(myMap)
````

This choropleth map doesn't inform clearly enough.
So let's try something else.

```{r second map, out.width="120%", echo = TRUE}

myMap2 <- ggplot(myRegions) + geom_sf(aes(fill=Regions,color = Regions))+
        scale_fill_brewer(palette="Set1")+
        labs(caption="Number of Scholarships Given by World Region in 2016", 
             title="World Repartition of French Government Scholarships")+
        geom_label(aes(x=LON, y=LAT), 
                   color="black", fill = "seashell", 
                   label=myRegions$schol, size=1.8)+
        xlab("") + ylab("")

print(myMap2)

````
